IRTF Spectro-Photometry of Rotating Brown Dwarfs

### 2016-11-02 ms.tex
Updates from ShareLaTeX

\usepackage{natbib}
\usepackage[caption=false]{subfig}
\newcommand{\vdag}{(v)^\dagger}

@@

\author{E. Schlawin, A. Burgasser, J. Teske, J. Gizis, T. Karalidi }
\affil{Steward Observatory, Tucson AZ 85721, UCSD, DTM, University of Delaware}
\email{eas342@email.arizona.edu}

@@

\section{Introduction}

Brown dwarfs atmospheres are an intriguing environment to explore cloud composition, particle size and formation that also complement studies of exoplanet atmospheres.

The cloud layers may be studied from the direct spectroscopy and photometry of large populations of brown dwarf atmospheres.

In addition to the direct spectroscopy and photometry, brown dwarfs may be observed over their rotation periods to understand the spatial cloud structure and composition, that can change rapidly with time.

The photometry brown dwarfs at the L/T transition is explained by (silicate?) clouds at a temperature of (?).

L dwarfs are found to be variable with periods of 1-100 hours \citep{bailer-jones1999bdvar,bailer-jones1999varevo}.
This variability is explained by a patchy clouds at the L/T transition \citep{marley2010patchyc}.

\citep{burgaser2014irtf} first demonstrated that the Infrared Telescope Facility (IRTF) was a useful tool for characterizing brown dwarf variability and that a simultaneous reference can be used to correct for common-mode variability, such as telluric transmission variations.

We observed the three brown dwarfs as part of a pilot program to assess the efficacy of IRTF for measuring spectral variability in brown dwarf atmospheres.
2MASS J18212815+1414010 is an L5 brown dwarf showing a triangular H-band spectrum \citep{looper2008peculiarLdwarfs}.
2MASS J1821's short rotation period (4.2 hr) allows for time series spectroscopy for all longitudes in a single ground based observation night.
2MASS J08354256-0819237 \citep{cruz2003coolNeighbors} is also an L5 brown dwarf known to be variable.

\begin{table*}
\begin{center}
\begin{tabular}{cccc}
Name & Rotation Period & Spectral Type & K magnitude \\
-- & hr & -- & -- \\
\hline \hline
2MASS J1821+14010 & 4.2\footnote{\citet{metchev2015weatherII}} & L4.5 & 11.14 \\
2MASS J0835-019 & 9 & L5 & 11.65 \\
\end{tabular}
\end{center}
\end{table*}

\section{Observations}

For 2MASS J0835, we observed a simultaneous reference - 2MASS 08354383-0819212, $J$=12.74, $H$=12.28, $K_S$=12.19 at a distance of 28 arcsec.
We obtained spectrophotometry over 4.65 hours, covering about half of a rotation period for 2MASS J0835.

We observed 2MASS J1821 and 2MASS J0835 for one night each with the IRTF.
For 2MASS J1821, we observed a simultaneous reference - 2MASS 18212622+1414064, $J$=12.58, $H$=11.97, $K_S$=11.82  at a distance of 24\arcsec.
We were able to measure spectrophotometry over 7.47 hours, which was 1.8 rotations at the 4.2 rotation period from \citet{metchev2015weatherII}.

As visible in Figure \ref{fig:specphot1821}, the light curves for 2MASS J1821 repeat the same fluctuations after one rotation period.
Assuming the brown dwarfs cloud structure was relatively unchanged in one rotation, this enabled confirmation that the signal was astrophysical as opposed to the systematics affecting the same instrument telescope for observations of the  KIC 12557548 system \citep{schlawin2016kic1255}.
%Using MORIS image for distance and plate scale in header of 0.1143 arcsec/px

%Using SpeX Guider image for distance of 241px  and plate scale in header of 0.116 arcsec/px

We use the same method as \citet{schlawin2014} to obtain high precision spectrophotometry.
We used a 0.9~$\mu$m dichoric to split the optical wavelengths to the MORIS imager \citep{Gulbis2011}.
For guiding, we use the MORIS imager in the SDSS $i$ band and 60 second long exposures in order to obtain simultaneous photometry on 2MASS J1821.
For 2MASS J0835, we were unable to obtain photometry - why? due to the fainter source?

\begin{table*}
\begin{center}
\caption{Observing Parameters}\label{tab:obsParam}
\begin{tabular}{ccccc}
Target & Observing Date & N$_{int}$ & t$_{exp}$ & Reference Star \\
-- & UT Start & -- & (s) & -- \\
\hline
2MASS J1821 & 2015-12-31 & 363 & 45 & 2MASS 18212622+1414064 \\
2MASS J0835 & 2016-06-25 & 352 & 60 & 2MASS 08354383-0819212 \\
\end{tabular}
\end{center}
\tablenotetext{}{}
\end{table*}

We observed 2MASS J1821 and J0835 each for one night as part of a pilot program to explore a variety of brown dwarfs with different variability levels and atmospheric temperatures.
Table \ref{tab:obsParam} shows the observing parameters for each target including the integration time, number of integrations and reference star.

Wavelength calibrations were performed with a 0.3$\times$60\arcsec\ slit and an argon emission lamp.
We performed calibrations sequences of argon emission lamp spectra and flat fielding with the 3$\times$60\arcsec\ slit both before and after the brown dwarf time series to obtain information on the flat field and any flexure in the instrument with telescope orientation.

For 2MASS J0835, we use a combination of an incandescent lamp and a sky frame to construct a flat.
Due to flexure and motion with thin the system, we use a sky frame to get the structure of the background with low order polynomials fits in the horizontal direction.
All of the (large $\gtrsim$ 30 px) structure is removed from the lamp frame with low order polynomials, and this residual flat is used to correct the pixel-to-pixel variations while the sky frame is used to measure the larger structures.
We cross-correlate the sky frame with each image to account for any spatial shifts and apply the pixel-to-pixel flat to construct a custom flat field for every image.

For 2MASS J1821, we did not have sufficient sky frames for sky flats so we use an incandescent lamp for flat fielding.
Here, we fit the flat field structure with low order polynomials in the incandescent flat field to describe the spatial structure and use the residual image as a pixel-to-pixel flat.
As in 2MASS J0835, we cross-correlate the spatial structure image to find a shift and then multiply it by the pixel-to-pixel flat to create a custom flat field for every image.
In both 2MASS J0835 and 2MASS J1821 we remove all spectral structure from the flat fields to make ``response'' images that do not include the spectral structure of the lamp or dramatically alter the flux levels that would affect SNR calculations from the number of photo-electrons in a given pixel.

As in \citep{schlawin2016kic1255}, we perform background subtraction over the entire slit with polynomial fit.
We use a 4th order polynomial through all points outside +/-30 pixels of each aperture for the background subtraction.

\section{Light Curves}

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{specphot_j0835.pdf}
	\label{fig:specphot0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{specphot_j1821.pdf}
	\label{fig:specphot1821}
	}
	\caption{Top Panels: The target stars' median raw spectrum compared with the reference star. The areas near 1.4 and 1.8 $\mu$m are contaminated by telluric water absorption. The reference stars are significantly higher temperatures. Bottom Panels: Dynamic spectrum of 2MASS J1821.}
	\label{fig:specphot}
\end{figure*}

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{2mass_0835_t_series.pdf}
	\label{fig:tserPhase0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_t_series.pdf}
	\label{fig:tserPhase1821}
	}
	\caption{Phase folded time series for both systems.}
	\label{fig:tserPfold}
\end{figure*}

\begin{figure}[!ht]
\centering
\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821.pdf}
\caption{Sine fit amplitude versus wavelength for 2MASS J1821. The regions at 1.4~$\mu$m and 1.9~$\mu$m are contaminated by telluric absorption so the variations can likely be due to telluric variability not corrected by the reference star.}\label{fig:DHSRes}
\end{figure}

@@

\section{Acknowledgements}
%If  used, this work made use of the \texttt{astropy} package \citep{astropy2013}.
%If used, some data was collected from the Open Exoplanet Catalogue \citep{rein2012openExoCat}.

>>>>

\usepackage{natbib}

\newcommand{\vdag}{(v)^\dagger}

@@

\author{E. Schlawin, A. Burgasser, J. Teske, J. Gizis, T. Karalidi? }
\affil{Steward Observatory, Tucson AZ 85721, UCSD, DTM, University of Delaware}
\email{eas342@email.arizona.edu}

%This is a test by Gizis

@@

\section{Introduction}
\citep{burgaser2014irtf}.

\section{Light Curves}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.5\textwidth]{2mass_1821_t_series.pdf}
\caption{Time Series.}\label{fig:DHSRes}
\end{figure}

@@

\section{Acknowledgements}

%If used, some data was collected from the Open Exoplanet Catalogue \citep{rein2012openExoCat}.
